Total Score

### 2023-01-30 src/MSAtotal_scores.Rmd
tested different criteria weights, weighting climate risk as the highest

```{r}
# weight criteria for Owen
criteria_weights_owen <- c(0.37, 0.12, 0.22, 0.07, 0.0, 0.07, 0.15)

@@

```{r}
# weight criteria for students
criteria_weights_students <- c(0.21, 0.0, 0.12, 0.17, 0.16, 0.17, 0.17)

@@

>>>>

```{r original weights}
# weight criteria for Owen
criteria_weights_owen <- c(0.37, 0.12, 0.22, 0.07, 0.0, 0.07, 0.15)

@@

```{r student weights}
# weight criteria for students
criteria_weights_students <- c(0.21, 0.0, 0.12, 0.17, 0.16, 0.17, 0.17)

@@

```{r climate risk weighted 50 and other 0.1}
# weight criteria for Owen
weights_climate50 <- c(0.1, 0.1, 0.1, 0.1, 0.0, 0.1, 0.50)

#make landlord_score column
criteria_all <- criteria_all %>% 
  mutate(score_climate50 = cbsa, #this is just a place holder
         real_estate_score = as.numeric(real_estate_score),
         landlord_score = as.numeric(landlord_score)
  )

size <- dim(criteria_all)
for (i in 1:size[1]) {
  cbsa_data <- c(criteria_all$real_estate_score[i],
                criteria_all$landlord_score[i],
                 criteria_all$normalized_irr[i],
                 criteria_all$inverted_n_total_co2[i],
                criteria_all$inverted_n_health_emissions_cost[i],
                criteria_all$normalized_annual_renewable[i],
                criteria_all$normalized_inverted_climate_risk[i]
                  )
  criteria_all$score_climate50[i] = weighted.mean(cbsa_data, weights_climate50)
}

```{r climate risk 40 }
# weight criteria for Owen
weights_climate40 <- c(0.15, 0.1, 0.15, 0.1, 0.0, 0.1, 0.40)

#make landlord_score column
criteria_all <- criteria_all %>% 
  mutate(score_climate40 = cbsa, #this is just a place holder
         real_estate_score = as.numeric(real_estate_score),
         landlord_score = as.numeric(landlord_score)
  )

size <- dim(criteria_all)
for (i in 1:size[1]) {
  cbsa_data <- c(criteria_all$real_estate_score[i],
                criteria_all$landlord_score[i],
                 criteria_all$normalized_irr[i],
                 criteria_all$inverted_n_total_co2[i],
                criteria_all$inverted_n_health_emissions_cost[i],
                criteria_all$normalized_annual_renewable[i],
                criteria_all$normalized_inverted_climate_risk[i]
                  )
  criteria_all$score_climate40[i] = weighted.mean(cbsa_data, weights_climate40)
}
```

```{r climate risk 50 and proportional weights for others}
weights_climate50_prop <- c(0.18, 0.07, 0.11, 0.07, 0.0, 0.07, 0.50)

#make landlord_score column
criteria_all <- criteria_all %>% 
  mutate(score_climate50_prop = cbsa, #this is just a place holder
         real_estate_score = as.numeric(real_estate_score),
         landlord_score = as.numeric(landlord_score)
  )

size <- dim(criteria_all)
for (i in 1:size[1]) {
  cbsa_data <- c(criteria_all$real_estate_score[i],
                criteria_all$landlord_score[i],
                 criteria_all$normalized_irr[i],
                 criteria_all$inverted_n_total_co2[i],
                criteria_all$inverted_n_health_emissions_cost[i],
                criteria_all$normalized_annual_renewable[i],
                criteria_all$normalized_inverted_climate_risk[i]
                  )
  criteria_all$score_climate50_prop[i] = weighted.mean(cbsa_data, weights_climate50_prop)
}
```
